---
title: "NSW Gov Internship"
author: "Rinaldo Gagiano"
date: "25/11/2020"
output: pdf_document
---

```{r packages, include=FALSE,warning=FALSE,message=FALSE}
library(tidyverse)
library(readxl)
library(dplyr)
library(ggplot2)
library(tidyr)
```

```{r, include=FALSE,warning=FALSE,message=FALSE}
nswGov <- read_xlsx("NSWGov.xlsx",sheet=3)
```

# Prediction Analysis

## Representation Trends between Job Type and Gender through the year 2025

```{r include=TRUE,echo=FALSE,warning=FALSE,message=FALSE}
#Total Proportions Predictions 
OFF <- nswGov %>%
  filter(Gender == "Female") %>%
  filter(`PT/FT`=="Full-Time") %>%
  group_by(Year,`PT/FT`,Gender) %>%
  summarise("HC" = sum(Headcount))

OFP <- nswGov %>%
  filter(Gender == "Female") %>%
  filter(`PT/FT`=="Part-Time") %>%
  group_by(Year,`PT/FT`,Gender) %>%
  summarise("HC" = sum(Headcount))

OMF <- nswGov %>%
  filter(Gender == "Male") %>%
  filter(`PT/FT`=="Full-Time") %>%
  group_by(Year,`PT/FT`,Gender) %>%
  summarise("HC" = sum(Headcount))

OMP <- nswGov %>%
  filter(Gender == "Male") %>%
  filter(`PT/FT`=="Part-Time") %>%
  group_by(Year,`PT/FT`,Gender) %>%
  summarise("HC" = sum(Headcount))

time <- data.frame(c(2019:2025))
colnames(time) <- "Year"

OMFfit <-lm(HC ~ Year,data = OMF)
OMPfit <-lm(HC ~ Year,data = OMP)
OFFfit <-lm(HC ~ Year,data = OFF)
OFPfit <-lm(HC ~ Year,data = OFP)

FFP <- predict(OFFfit,time)
FPP <- predict(OFPfit,time)
MPP <- predict(OMPfit,time)
MFP <- predict(OMFfit,time)

OFF[c(6:12),1] <- time
OFF[,2] <- "Full-Time"
OFF[,3] <- "Female"
OFF[c(6:12),4] <- FFP

OFP[c(6:12),1] <- time
OFP[,2] <- "Part-Time"
OFP[,3] <- "Female"
OFP[c(6:12),4] <- FPP

OMF[c(6:12),1] <- time
OMF[,2] <- "Full-Time"
OMF[,3] <- "Male"
OMF[c(6:12),4] <- MFP

OMP[c(6:12),1] <- time
OMP[,2] <- "Part-Time"
OMP[,3] <- "Male"
OMP[c(6:12),4] <- MPP

Prop_Pred <- rbind(OFF,OFP,OMF,OMP)
plot_col <- c("#e6005c","#ff66a3","#0073e6","#66b3ff")
Prop_Pred %>%
  ggplot(aes(x=Year,y=`HC`,group=interaction(`PT/FT`,Gender),
             colour=interaction(`PT/FT`,Gender)))+
  annotate("rect",xmin=2013.5,xmax=2018.5,ymin=0,ymax=160000,
           fill="#4dff4d",alpha=0.5)+
  annotate("rect",xmin=2018.5,xmax=2025.5,ymin=0,ymax=160000,
           fill="#ff944d",alpha=0.5)+
  ggtitle("Employment Type Prediction (2014-2025)")+
  annotate("segment", x = 2018.5, xend = 2018.5, y= 0, yend = 160000,
           colour = "red", size = .5)+
  annotate("text",x=2018.3,y=55000,label="Prediction Begins",size=2.5,angle=90)+
  labs(y="Head Count",colour="Legend")+
  labs(caption="*F/T: Full-Time    P/T=Part-Time")+
  scale_color_manual(values=c(plot_col),labels=c("F/T Female","P/T Female",
                                                 "F/T Male","P/T Male"))+
  geom_line()+
  geom_point()
```

As seen above, 'Full-Time Males' are exhibiting a decline.

\pagebreak

## Male Full-Time Cluster Trends

```{r include=TRUE,echo=FALSE,warning=FALSE,message=FALSE}
nswGov %>%
  filter(Gender=="Male")%>%
  filter(`PT/FT`=="Full-Time") %>%
  group_by(Cluster,Year) %>%
  summarise("HC" = sum(Headcount)) %>%
  ggplot(aes(x=Year,y=HC,colour=Cluster,fill=Cluster))+
  geom_col()+
  facet_wrap(vars(Cluster),ncol=5,scales="free_y")+
  theme(axis.text.y = element_blank())+
  theme(axis.ticks.y = element_blank())+
  theme(axis.title.y = element_blank())+
  theme(strip.text.x = element_blank())+
  theme(axis.text.x = element_text(angle=90))
```

Each cluster plotted without a relative y-axis, gives insight into each trend. As seen from the plot, clusters with the greatest notable decline:

* Education
* Family & Community Services
* Finance, Services & Innovation
* Industry
* Treasury

## Specified Cluster Examinations

```{r include=TRUE,echo=FALSE,warning=FALSE,message=FALSE}
nswGov %>%
  filter(Gender=="Male")%>%
  filter(`PT/FT`=="Full-Time") %>%
  filter(!Cluster=="Health")%>%
  filter(!Cluster=="Justice")%>%
  filter(!Cluster=="Planning & Environment")%>%
  filter(!Cluster=="Premier & Cabinet")%>%
  filter(!Cluster=="Transport")%>%
  group_by(Cluster,Year) %>%
  summarise("Head Count" = sum(Headcount)) %>%
  ggplot(aes(x=Year,y=`Head Count`,colour=Cluster,fill=Cluster))+
  geom_col()+
  facet_wrap(vars(Cluster),ncol=5)+
  theme(strip.text.x = element_blank())+
  theme(axis.text.x = element_text(angle=90))
```

Another look at the specified clusters through a relative scale signifies which clusters are most at effect. Tabling these results will give mathematical insurance to significance:

```{r include=TRUE,echo=FALSE,warning=FALSE,message=FALSE}
MF_Cluster <- nswGov %>%
  filter(Year=="2014" | Year =="2018")%>%
  filter(Gender=="Male")%>%
  filter(`PT/FT`=="Full-Time") %>%
  filter(!Cluster=="Health")%>%
  filter(!Cluster=="Justice")%>%
  filter(!Cluster=="Planning & Environment")%>%
  filter(!Cluster=="Premier & Cabinet")%>%
  filter(!Cluster=="Transport")%>%
  group_by(Cluster,Year) %>%
  summarise("HC" = sum(Headcount)) %>%
  group_by(Cluster) %>%
  summarise("Total HC Change" = head(HC,2)-head(HC,1),
            "Total % Change" = 100-(head(HC,2)/head(HC,1)*100))

MF_Cluster <- MF_Cluster[c(seq(2,10, 2)),]
MF_Cluster
```

The tabling of the results, through Headcount change and percentage change, indicates which clusters are in need of focus. Looking at percentage change, clusters 'Family & Community Services' and 'Industry' must be analyzed. The total change also draws in the cluster 'Education'. 

## Education Agency Analysis

```{r include=TRUE,echo=FALSE,warning=FALSE,message=FALSE}
MF_Edu <- nswGov %>%
  filter(Gender=="Male") %>%
  filter(`PT/FT`=="Full-Time") %>%
  filter(Cluster == "Education")

MF_Edu %>%
  ggplot(aes(x=Year,y=Headcount,colour=Agency)) +
  geom_line()+
  geom_point()+
  facet_wrap(vars(Agency),ncol=4)+
  theme(axis.text.x = element_text(angle=90))
```

This plot indicates which agency, within its respective cluster, has the greatest size as well as decline, from this it can be determined:

* Education Agency 4 has the highest headcount and the greatest loss of people over the years

## Family & Community Services Agency Analysis

```{r include=TRUE,echo=FALSE,warning=FALSE,message=FALSE}
MF_FCS <- nswGov %>%
  filter(Gender=="Male") %>%
  filter(`PT/FT`=="Full-Time") %>%
  filter(Cluster == "Family & Community Services")

MF_FCS %>%
  ggplot(aes(x=Year,y=Headcount,colour=Agency)) +
  geom_line()+
  geom_point()+
  facet_wrap(vars(Agency),ncol=3)+
  theme(axis.text.x = element_text(angle=90))
```

* Family & Community Services Agency 1 has the highest headcount and the greatest loss of people over the years

## Industry Agency Analysis

```{r include=TRUE,echo=FALSE,warning=FALSE,message=FALSE}
MF_Ind <- nswGov %>%
  filter(Gender=="Male") %>%
  filter(`PT/FT`=="Full-Time") %>%
  filter(Cluster == "Industry")

MF_Ind %>%
  ggplot(aes(x=Year,y=Headcount,colour=Agency)) +
  geom_line()+
  geom_point()+
  facet_wrap(vars(Agency),ncol=4)+
  theme(axis.text.x = element_text(angle=90))
```

* Industry Agency 7 has the highest headcount and the greatest loss of people over the years

## Conclusion

When comparing representation of Job-Type and Gender, it can be identified that Male's working Full-Time are at a decline and will continue to do so, as seen through the prediction analysis. 

\ 

A proposed solution, drawn from in-depth analysis, is to  examine the following agencies with the highest decline in Male Full-Time Employees:

* Education Agency 4
* Family & Community Services Agency 1
* Industry Agency 7
















































































































